Cell Decompositions for Rank Two Quiver Grassmannians

### 2017-12-19 Grassmannian_cells.tex
reorganized section 5

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Quiver Grassmannians of $\widetilde{K(n)}$}
\label{QG}
\noindent 
We fix a natural number $n\geq 3$. We fix the following lifts $\tilde P_m$  of $P_m$ to the universal cover $\widetilde{K(n)}$. For $m=1$ we assume that $\dim (\tilde P_1)_{1,1}=1$ and $\dim (\tilde P_1)_{i,w}=0$ if $(i,w)\neq (1,1)$. Moreover, we assume that $\dim (\tilde P_2)_{2,1}=\dim (\tilde P_2)_{1,w}=1$ for $w=a_1,\ldots,a_n$ and $\dim (\tilde P_2)_{i,w}=0$ if $(i,w)\notin\{(2,1),(1,a_1),\ldots,(1,a_n)\}$. Recall that applying the reflection functor $\Sigma_i$ on $K(n)$ corresponds to applying $\tilde\Sigma_i:=\prod_{w\in W_Q}\Sigma_{(i,w)}$ on $\widetilde{K(n)}$. Moreover, sinks become sources and vice versa. For $m\geq 3$, we can build lifts $\tilde P_m$ recursively by applying reflection functors or as Auslander-Reiten translation, i.e. we have
\begin{align}\label{recursive}\tilde P_m=\tilde\Sigma_2 \tilde P_{m-1},\quad\tilde P_{m+1}=\tilde\Sigma_{1}\tilde\Sigma_2\tilde P_{m-1}=\tau^{-1} \tilde P_{m-1}\text{ for }m\geq 2.\end{align}
It is rather important that $\tilde P_{2m}$ and $\tilde P_{2m-1}$ live on two different components of the universal covering quiver.

\begin{remark}\begin{enumerate}
\item Note that the group $W_Q$ acts naturally on $\widetilde{K(n)}_0$ via translation, i.e. $w.(q,w')=(q,ww')$ inducing an action on $\Rep(\widetilde{K(n)})$. Up to this action a lift $\tilde P_m$ of $P_m$ is unique (on isomorphism classes).
\item Then we have 
$$\tilde P_{2l-1,i}:=a_i.\tilde P_{2l-1},\quad \tilde P_{2l,i}:=a_i^{-1}.\tilde P_{2l}$$
for all $l\geq 1$ and for $i=1,\ldots,n$. This can be checked straightforwardly for $l=1$ and follows in general when applying the identities (\ref{recursive}).

\item Note that, the lifts $\tilde P_m$ all have the same middle vertex $(i,1)$ where $i=1$ is $m$ is odd and $i=2$ if $m$ is even.
\end{enumerate}
\end{remark}

%To do so, we fix $m$ and the following notation can be seen as relative to $m$\footnote{do we need this?}.

Every representation $\tilde P_m$ has $n$ subrepresentation $\tilde P_{m-1,1},\ldots,\tilde P_{m-1,n}$. Each of them corresponds to one of the $n$ different arrows of $K(n)$.

\begin{example}\label{smallm}[The cases $m=2,3,4$]
\end{example}

The representation $\tilde P_2$ is given by the following coefficient quiver:

\begin{align*}\xymatrix@R10pt@C20pt{&&\bullet\\ \bullet\ar^{a_1}[rru]\ar^{a_{n}}[rrd] &&\vdots\\&&\bullet}\end{align*}
The coefficient quiver of $\tilde P_2^{(i)}$, which we denote by $\mathcal A_i$ during this proof, can be obtained from this quiver by erasing the arrow $a_i$ and the corresponding sink. In turn, the quiver of $\tilde P_2^{(j_1,\ldots,j_l)}$ is obtained by erasing the arrows $a_{j_1},\ldots, a_{j_l}$.

Using this notation, we obtain that $\tilde P_3$ can be written as
	\begin{align*}\xymatrix@R10pt@C20pt{&&\mathcal A_1\ar_{a_{1}}[lld]\\ n-1 &&\vdots\\&&\mathcal A_n\ar_{a_{n}}[llu]}\end{align*}
	and, moreover, $\tilde P_3^{\uj}$ is obtained when erasing the subquiver $\mathcal A_{j_1},\ldots,\mathcal A_{j_l}$ and decreasing the dimension of the sink by one.  The Auslander-Reiten translate $\tau\tilde P_{3}^{(j_1,\ldots,j_l)}$ is given by
	\begin{align*}\xymatrix@R10pt@C20pt{&&\bullet\ar_{a_{j_1}}[lld]\\\bullet &&\vdots\\&&\bullet\ar_{a_{j_l}}[llu]}\end{align*}
In particular, the image of the unique homomorphism $\tilde P_{2,j_l}=a_{j_l}.\tilde P_2\to\tau\tilde P_{3}^{(j_1,\ldots,j_l)}$ has image $\bullet\xrightarrow{a_{j_l}}\bullet$.

The support of $\tilde P_4$ is given by
\[\xymatrix@R40pt@C10pt{&&&&&&n-1\ar^{a_1}[llllld]\ar^{a_2}[ld]\ar^{a_n}[rrrrd]&&&&&\\&2n-3&&&&2n-3&&\hdots&&&2n-3\\
\mathcal A_2\ar^{a_2}[ru]&\hdots&\mathcal A_n\ar^{a_n}[lu]&\mathcal A_1\ar^{a_1}[rru]&\widehat{\mathcal A_2}&\mathcal A_3\ar[u]^{a_3}&\hdots&\mathcal A_n\ar^{a_n}[llu]	&\hdots&\mathcal A_2\ar^{a_2}[ru]&\hdots&\mathcal A_{n-1}\ar^{a_{n-1}}[lu]}\]
where the numbers correspond to the dimensions of the respective vertices. Moreover, all dimensions on the subquivers $\mathcal A_i$ are one. The arrows connecting a quiver $\mathcal A_i$ to a sink of the remaining quiver start at the unique source of $\mathcal A_i$. Now $\tilde P_{3,l}$ can be found as the representation corresponding to the subquiver
\[\xymatrix@R40pt@C10pt{&&&&&&1\ar^{a_1}[llllld]\ar^{a_{l-1}}[ld]\ar^{a_l}[d]\ar^{a_{l+1}}[rd]\ar^{a_n}[rrrrd]&&&&&\\&1&&\hdots&&1&n-1&1&\hdots&&&1\\
&&&\mathcal A_1\ar^{a_1}[rrru]&\hdots&\mathcal A_{l-1}\ar_{a_{l-1}}[ru]&\widehat{\mathcal A_l}&\mathcal A_{l+1}\ar_{a_{l+1}}[lu]&\hdots&\mathcal A_n\ar_{a_n}[lllu]	&&&&}\]

Finally, the quiver corresponding to $\tilde P_4^{(1,\ldots,l)}$ is given by

\[\xymatrix@R45pt@C10pt{&&&&&&n-1-l\ar_{a_1}[llllld]\ar^{a_{l}}[llld]\ar^{a_{l+1}}[lld]\ar^{a_n}[rrrrd]&&&&&\\&n-1-l&\hdots&n-1-l&2n-3-l&&\hdots&&\hdots&&2n-3-l\\
&\mathcal A_1\ar^{a_1}[rrru]&\hdots&\mathcal A_l\ar[ru]^{a_l}&\widehat{A}_{l+1}&\mathcal A_{l+2}\ar^{a_{l+2}}[lu]	&\hdots&\mathcal A_n\ar^{a_n}[lllu]&&\mathcal A_2\ar^{a_2}[ru]&\hdots&\mathcal A_{n-1}\ar^{a_{n-1}}[lu]}\]
Now it is straightforward to see that $\tau \tilde P_4^{(1,\ldots,l)}=\tilde P_2^{(1,\ldots,l)}$, where $\tau^{-1}$ is given by reflecting at all the sinks first and at all sources afterwards. Actually, $\tilde P_2^{(1,\ldots,l)}$  is supported at the source lying in the upper row and the $n-l$ sinks connected to it by the arrows $a_{l+1},\ldots,a_n$.

@@

The next step is to introduce notation in order to locate truncated preprojectives as quotients of other truncated preprojectives in the universal covering for general $m$.
With every sequence of natural numbers $\ui=(i_1,\ldots,i_k)$ with $i_j\leq n$ and $k\leq m-1$, we can associate a preprojective subrepresentation $\tilde P_{m-k,\uj}$ of dimension $(u_{m-k},u_{m-k-1})$. More detailed, we obtain a sequence of preprojective representations 
$$\tilde P_{m-k,\ui}\subset P_{m-k+1,(i_1,\ldots,i_{k-1})}\subset\ldots\subset P_{m-1,(i_1,i_2)}\subset P_{m-1,i_1}\subset P_{m}.$$

Let
$$I^n_l:=\{(j_1,\ldots,j_{l})\mid j_i\in\{1,\ldots,n\},\,j_i\neq j_k\text{ if }i\neq k\}.$$
As we fixed the number of arrows, we drop the $n$ in what follows. For $\uj=(j_1,\ldots,j_{n-1})\in I_{n-1}$, let $j^c\in \{1,\ldots,n\}$ and $\uj^c=(j^c)$ where $j^c\neq j_i$ for $i=1,\ldots,n-1$. Clearly, $\uj^c$ is uniquely determined by $\uj$.

\begin{definition}Let ${\bf j}:=(\underline{j_1},\underline{j_2},\ldots,\underline{j_r})$ be a sequence with $\underline{j_1}\in I_{n-1}$, $\underline{j_2},\ldots,\underline{j_{r-1}}\in I_{n-2}$ and $\underline{j_r}\in I_s$ for $s\leq n-2$. Define $j_1^c$ as before.
 We say that ${\bf j}$ is admissible if 
$$ j_{k,i}\neq j_{k-1}^{c}\text{ for all }k=2,\ldots, r-1,\,i=1,\ldots,n-2\text{ and for }i=1,\ldots,s\text{ if }k=r$$
where $j_k^c\in\{1,\ldots,n\}$ for $2\leq k\leq r-1$ is recursively defined as the unique number satisfying $j_k^c\neq j_{k,i}$ for $i=1,\ldots,n-2$ and $j_k^c\neq j_{k-1}^c$. 
\end{definition}

For $\uj\in I_{l}$ with $l\leq n-1$, there exist unique short exact sequences 
\[\ses{\bigoplus_{i=1}^l\tilde P_{m-1,j_i}}{\tilde P_m}{\tilde P_{m}^{\uj}},\quad\quad\ses{\tilde P_{m-1,j_l}}{\tilde P_{m}^{(j_1,\ldots,j_{l-1})}}{\tilde P_{m}^{\uj}}\]
where the $\tilde P_m^{\uj}$ are lifts of truncated preprojectives (as defined in the last section). The next step is to define a unique truncated preprojective representation for each admissible sequence ${\bf j}=(\underline{j_1},\underline{j_2},\ldots,\underline{j_r})$. We define the admissible sequence $\delta {\bf j}$ (of length $r-1$) by
\[\delta {\bf j}:=((j_1^c,\underline{j_2}),\ldots,\underline{j_r}).\]
We recursively define $\delta^i{\bf j}$ for $i=1,\dots,r-1$.
%In the following, we assume without loss of generality that $i_1< i_2<\ldots< i_k$.
Note that we have $\delta\uj=(j^c)$ for $\uj\in I_{n-1}$.

\begin{lemma}The following holds:
  \label{le:preprojective lifts}
  \begin{enumerate}
    \item For $m\geq 2$, we have $\Hom_Q(P_{m-1},P_m)\cong\bigoplus_{i=1}^n \Hom_{\tilde Q}(\tilde P_{m-1,i},\tilde P_m)$, where each $\Hom_{\tilde Q}(\tilde P_{m-1,i},\tilde P_m)$ is one-dimensional;
   % \item For any proper subset $\{i_1,\ldots,i_k\}\subset\{1,\ldots,n\}$, there exists a short exact sequence
   %   \[0\longrightarrow \tilde P_{m-1,i_1}\oplus\cdots\oplus\tilde P_{m-1,i_k}\longrightarrow\tilde P_m\longrightarrow \tilde P_m^{i_1,\ldots,i_k}\longrightarrow 0;\]
    \item For $m\geq 1$, the representations $\tilde P_{m,i}$ are pairwise orthogonal, i.e. for $i\neq k$ we have $$\Hom(\tilde P_{m,i},\tilde P_{m,k})=\Ext(\tilde P_{m,i},\tilde P_{m,k})=0;$$
    \item If $\uj\in I_{n-1}$ and $m\geq 3$, we have $\tilde P_{m}^{\uj}\cong \tilde P_{m-1,j^c}^{\uj^c}= \tilde P_{m-1,j^c}/\tilde P_{m-2,(j^c,j^c)}$.
		\item Let $m\geq 3$ and $1\leq r\leq m-1$ and let $\mathbf j:=(\underline{j_1},\ldots,\underline{j_r})$ be an admissible sequence. Let ${\bf j}(k):=(\underline{j_1},\ldots,\underline{j_k})$ for $k=2,\ldots,r-1$. Then we recursively have
		\[\tilde P_{m-l,(j_1^c,\ldots,j_k^c)}^{\delta^k{\bf j(k)}}=\tilde P_{m-l+1,(j_1^c,\ldots,j_{k-1}^c)}^{\delta^{k-1}\bf j(k)}\]
		for $k=1,\ldots,r$. Thus we can associate a unique truncated preprojective representation $$\tilde P^{\mathbf j}_{m-r+1}:=\tilde P_{m-r+1,(j_1^c,\ldots,j_{r-1}^c)}^{(j_{r-1}^c,j_{r,1},\ldots,j_{r,s})}$$%/\tilde P_{m-r+1,(j_1^c,\ldots,j_{r-1}^c)}$$ 
		with each admissible sequence ${\bf j}$.
  \end{enumerate}
\end{lemma}
\begin{proof}
The first statement follows from Theorem \ref{covering}. For $m=1$, the second part is obvious. For $m\geq 2$, it then follows by applying the identities (\ref{recursive}).

To prove the third part, we consider the following commutative diagram where the square on the left hand side is the corresponding Auslander-Reiten sequence:
\[\xymatrix{0\ar[r] &\bigoplus_{i=1}^{n-1}\tilde P_{m-1,j_i}\ar[r] &  \tilde P_{m}\ar[r] & \tilde P_{m}^{\uj}\ar[r] & 0 \\
  0\ar[r]&\tau\tilde P_m=\tilde P_{m-2} \ar[r]\ar[u] & \tilde P_{m-1,j^c}\ar[u]\ar[r]& \tilde P_{m}^{\uj}\ar[r]\ar@{=}[u]& 0}\]

%Thus we see that $\tilde P_{m}^{\ui}\cong \tilde P_{m-1}^{(l)}$ for some $l\in\{1,\ldots,n\}$. But now it is straightforward to check that $l=n$. \footnote{more precise?} 
For $m=3$, is straightforward that the injection of the lower row factors over $\tilde P_{1,j^c}$ which means that we get the same commutative diagram when replacing $\tilde P_{1}$ by $\tilde P_{1,(j^c,j^c)}$. Thus we have $\tilde P_{3}^{\ui}\cong \tilde P_{2,j^c}^{\uj^c}$. Applying the identities (\ref{recursive}) the claim follows for $m\geq 3$.

The forth statement is now obtained recursively when initially considering the commutative diagram from above replacing $\uj$ by $\underline{j_1}$. We have $\delta^{k-1}{\bf j}(k)=(j_{k-1}^c,j_{k,1},\ldots,j_{k,n-1})$. We use the third statement in order to successively obtain commutative diagrams
\[\xymatrix{0\ar[r] &\bigoplus_{i=1}^{n-2}\tilde P_{m-k,(j_1^c,\ldots,j_{k-1}^c,j_{k,i})}\ar[r] &  \tilde P^{(j_{k-1}^c)}_{m-k+1,(j_1^c,\ldots,j_{k-1}^c)}\ar[r] & \tilde P_{m-k+1,(j_1^c,\ldots,j_{k-1}^c)}^{\delta^{k-1}{\bf j}(k)}\ar[r] & 0 \\
  0\ar[r]&\tilde P_{m-(k+1),(j_1^c,\ldots,j_{k}^c,j_k^c)} \ar[r]\ar[u] & \tilde P_{m-k,(j_1^c,\ldots,j_{k}^c)}\ar[u]\ar[r]& \tilde P_{m-k,(j_1^c,\ldots,j_{k}^c)}^{(j_{k}^c)}\ar[r]\ar@{=}[u]& 0}\]
Now we have $\delta^{k-1}{\bf j}(k)=(j_k^c)$.	Finally, we consider the short exact sequence:

\[\xymatrix{0\ar[r] &\bigoplus_{i=1}^{s}\tilde P_{m-r,(j_1^c,\ldots,j_{r-1}^c,j_{r,i})}\ar[r] &  \tilde P^{(j_{r-1}^c)}_{m-r+1,(j_1^c,\ldots,j_{r-1}^c)}\ar[r] & \tilde P_{m-r+1,(j_1^c,\ldots,j_{r-1}^c)}^{{\bf j}}\ar[r] & 0 }.\]
As $\Hom(\tilde P_{m-k,(j_1^c,\ldots,j_{k-1}^c,j_{k,i})},\tilde P_{m-k+1,(j_1^c,\ldots,j_{k-1}^c)})=\kk$ for all $k=2,\ldots,r$ and $i=1,\ldots,n-1$, applying the second statement, we obtain that the quotient $\tilde P_{m-r+1}^{\bf j}$ is uniquely determined.
	\end{proof}
We denote the quotient morphism by $\pi_m^{\bf j}:\tilde P_m\to \tilde P_{m-r+1}^{\bf j}$. Let $\ui=(i_{1},\ldots,i_{l})$. It is important for us that this morphism factors through all truncated preprojectives $\tilde P_m^{\ui}$ where $l\leq n-1$ and $i_k\neq j_1^c$ for $k=1,\ldots, l$. We denote the quotient morphism from $\tilde P_m^{\ui}$ to $\tilde P_{m-r+1}^{\bf j}$ by $\pi_{m,\ui}^{\bf j}$.

Our construction immediately yields the following lemma.
\begin{lemma}\label{projections}
Let $\tilde P_m$ be a lift of the preprojective representation $P_m$ and let ${\bf j}=(\underline{j_1},\ldots,\underline{j_r})$ with $r\leq m-1$ and $\underline{j_r}\in I_s$ be an admissible sequence with entries $j_{k,i}$ for $k=1,\ldots r$. Then we have
\[\pi_m^{\bf j}=\pi_{m-r+1,j_{r-1}^c}^{\underline{j_r}}\circ\ldots\circ\pi^{\underline{j_2}}_{m-1,j_1^c}\circ\pi_m^{\underline{j_1}}\]
and, for any sequence $(l_1,\ldots,l_{n-2})\in I_{n-2}$, we have
\[\pi_{m-k+1,j_{k-1}^c}^{\underline{j_k}}=\prod_{i=1}^{n-2} \pi^{j_{k,l_{i}}}_{m-k+1,(j_{k-1}^c,j_{k,l_1},\ldots,j_{k,l_{i-1}})}\]
for $k=1,\ldots,r-1$ where $\pi_{m,j_{-1}^c}^{\underline{j_1}}:=\pi_m^{\underline{j_1}}$ and the analogous statement for $\pi_{m-r+1,j_{r-1}^c}^{\underline{j_r}}$ and $(l_1,\ldots,l_{s-1})\in I_{s-1}$ holds.
\end{lemma}
We want to apply $\pi_m^{\bf j}$ also to translated representations $w.\tilde P_m$, mostly for $w\in\{a_i,a_i^{-1}\}$. Therefore, we need to apply a translated version of this morphism. In abuse of notation, we also denote this morphism $\pi_m^{\bf j}$.

 We need the following lemma analyzing the possible subrepresentations of truncated preprojective representations.
\begin{lemma}\label{le:subrep}
   All nontrivial proper subrepresentations $U$ of $\tilde P_m^{(i_1,\ldots,i_l)}$ are preprojective.	\footnote{Does it follow that the representations $F_{K(m)}\tilde P_m^{(j_1,\ldots,j_l)}$ are quasi-simple?}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Quiver Grassmannians of $\widetilde{K(n)}$}
\label{QG}
\noindent 
We fix a natural number $n\geq 3$. We fix the following lifts $\tilde P_m$  of $P_m$ to the universal cover $\widetilde{K(n)}$. For $m=1$ we assume that $\dim (\tilde P_1)_{1,1}=1$ and $\dim (\tilde P_1)_{i,w}=0$ if $(i,w)\neq (1,1)$. Moreover, we assume that $\dim (\tilde P_2)_{2,1}=\dim (\tilde P_2)_{1,w}=1$ for $w=a_1,\ldots,a_n$ and $\dim (\tilde P_2)_{i,w}=0$ if $(i,w)\notin\{(2,1),(1,a_1),\ldots,(1,a_n)\}$. Recall that applying the reflection functor $\Sigma_i$ on $K(n)$ corresponds to applying $\tilde\Sigma_i:=\prod_{w\in W_Q}\Sigma_{(i,w)}$ on $\widetilde{K(n)}$. Moreover, sinks become sources and vice versa. For $m\geq 2$, we can build lifts $\tilde P_m$ recursively by applying reflection functors or as Auslander-Reiten translation, i.e. we have
\begin{align}\label{recursive}\tilde P_m=\tilde\Sigma_2 \tilde P_{m-1},\quad\tilde P_{m+1}=\tilde\Sigma_{1}\tilde\Sigma_2\tilde P_{m-1}=\tau^{-1} \tilde P_{m-1}.\end{align}
It is rather important that $\tilde P_{2l}$ and $\tilde P_{2l-1}$ live on two different components of the universal covering quiver.

\begin{remark}\begin{enumerate}
\item Note that the group $W_Q$ acts naturally on $\widetilde{K(n)}_0$ via translation, i.e. $w.(q,w')=(q,ww')$ inducing an action on $\Rep(\widetilde{K(n)})$.

%Up to this action a lift $\tilde P_m$ of $P_m$ is unique (on isomorphism classes).
\item We have 
$$\tilde P_{2l-1,i}:=a_i.\tilde P_{2l-1},\quad \tilde P_{2l,i}:=a_i^{-1}.\tilde P_{2l}$$
for all $l\geq 1$ and for $i=1,\ldots,n$. This can be checked straightforwardly for $l=1$ and follows in general when applying the identities (\ref{recursive}).

Now every representation $\tilde P_m$ has $n$ subrepresentation $\tilde P_{m-1,1},\ldots,\tilde P_{m-1,n}$. Each of them corresponds to one of the $n$ different arrows of $K(n)$.

\item Note that, the dimension vector of $\tilde P_m$ are symmetric. They all have the same middle vertex $(1,1)$ if $m$ is odd and $(2,1)$ if $m$ is even.
\end{enumerate}
\end{remark}
Let
$$I^n_l:=\{(j_1,\ldots,j_{l})\mid j_i\in\{1,\ldots,n\},\,j_i\neq j_k\text{ if }i\neq k\}.$$
As we fixed the number of arrows, we drop the $n$ in what follows.

With every sequence of natural numbers $\ui=(i_1,\ldots,i_k)$ with $i_j\leq n$ and $k\leq m-1$, we can associate a preprojective subrepresentation $\tilde P_{m-k,\uj}$ of dimension $(u_{m-k},u_{m-k-1})$. More detailed, we obtain a sequence of preprojective representations 
$$\tilde P_{m-k,\ui}\subset \tilde P_{m-k+1,(i_1,\ldots,i_{k-1})}\subset\ldots\subset \tilde P_{m-2,(i_1,i_2)}\subset \tilde P_{m-1,i_1}\subset\tilde P_{m}.$$

\begin{lemma}\label{le:properties}The following holds:
\begin{enumerate}
 \item For $m\geq 2$, we have $\Hom_Q(P_{m-1},P_m)\cong\bigoplus_{i=1}^n \Hom_{\tilde Q}(\tilde P_{m-1,i},\tilde P_m)$, where each $\Hom_{\tilde Q}(\tilde P_{m-1,i},\tilde P_m)$ is one-dimensional;
   % \item For any proper subset $\{i_1,\ldots,i_k\}\subset\{1,\ldots,n\}$, there exists a short exact sequence
   %   \[0\longrightarrow \tilde P_{m-1,i_1}\oplus\cdots\oplus\tilde P_{m-1,i_k}\longrightarrow\tilde P_m\longrightarrow \tilde P_m^{i_1,\ldots,i_k}\longrightarrow 0;\]
    \item For $m\geq 1$, the representations $\tilde P_{m,i}$ are pairwise orthogonal, i.e. for $i\neq k$ we have $$\Hom(\tilde P_{m,i},\tilde P_{m,k})=\Ext(\tilde P_{m,i},\tilde P_{m,k})=0;$$
		\item For every $\uj\in I_l$, there exists a truncated preprojective representation $\tilde P_{m}^{\uj}$ which is the cokernel of
		\[\ses{\bigoplus_{i=1}^l \tilde P_{m-1,j_i}}{\tilde P_m}{\tilde P_{m}^{\uj}}.\]
		On the universal covering, we have $\Hom(\tilde P_{m-1,k},\tilde P_m)\cong\Hom(\tilde P_{m-1,k},\tilde P_m^{\uj})=\kk$  where $k\neq j_i$ for $i=1,\ldots,l$, $\Hom(\tilde P_m,\tilde P_m^{\uj})=\kk$, $\Ext(\tilde P_{m},\tilde P_{m}^{\uj})=0$ and $\Ext(\tilde P_{m}^{\uj},\tilde P_{m}^{\uj})=0$.

		\end{enumerate}
\end{lemma} 
\begin{proof}The first statement follows from Theorem \ref{covering}. For $m=1$, the second part is obvious. For $m\geq 2$, it then follows by applying the identities (\ref{recursive}).

The first identity of the last statement follows when applying $\Hom(\tilde P_{m-1,k},\underline{\quad})$ to the short exact sequence under consideration together with the first statement of this lemma.

As $\Ext(\tilde P_{m},\tilde P_{m-1,j_i})=\Hom(\tilde P_{m},\tilde P_{m-1,j_i})=0$ and $\Hom(\tilde P_m,\tilde P_m)=\kk$, the second and third identity follows when applying $\Hom(\tilde P_{m},\underline{\quad})$.

For every $i=1,\ldots,l$, we have $\Hom(\tilde P_{m-1,j_i},\bigoplus_{i=1}^l \tilde P_{m-1,j_i})\cong\Hom(\tilde P_{m-1,j_i},\tilde P_m)=\kk$. Thus it follows that $\Hom(\bigoplus_{i=1}^l \tilde P_{m-1,j_i},\tilde P^{\uj}_{m})=0$ because the representations $\tilde P_{m-1,j_i}$ are exceptional. Thus we obtain the last identity when applying $\Hom(\underline{\quad},\tilde P^{\uj}_{m})$.

\end{proof} 
%To do so, we fix $m$ and the following notation can be seen as relative to $m$\footnote{do we need this?}.

In the same way as for the preprojective lifts $\tilde P_{m-k}$, we can define truncated preprojective quotients $\tilde P_{m-k,\ui}^{\uj}$ of $\tilde P_{m-k,\ui}$ where $\uj\in I_s$ with $s\leq n-1$. Therefore, we quotient out the translations of $\tilde P_{m-k-1,(\ui,j_t)}$ for $t=1,\ldots,s$. These quotients are unique in the sense that $\Hom(\tilde P_{m-k,\ui},\tilde P_{m-k,\ui}^{\uj})=\kk$.

\begin{example}\label{smallm}[The cases $m=2,3,4$]
\end{example}
As the lifts of all (truncated) preprojectives are exceptional as representations of $\widetilde{K(m)}$, they are uniquely determined by its dimension vector. We use this fact and do not state the particular maps defining the lifts. In this example, we just state the support of the representation including those dimensions which are not one. We call it the quiver of the representations.

The representation $\tilde P_2$ is defined by the following quiver:

\begin{align*}\xymatrix@R10pt@C20pt{&&(1,a_1)\\(2,1)\ar^{a_1}[rru]\ar^{a_{n}}[rrd] &&\vdots\\&&(1,a_n)}\end{align*}
The support of $\tilde P_2^{(i)}$, which we denote by $\mathcal A_i$ during this proof, can be obtained from this quiver by erasing the arrow $a_i$ and the corresponding sink. In turn, the quiver of $\tilde P_2^{(j_1,\ldots,j_l)}$ is obtained by erasing the arrows $a_{j_1},\ldots, a_{j_l}$.

The representation $\tilde P_3$ is given by the quiver
	\begin{align*}\xymatrix@R10pt@C20pt{&&\mathcal A_1\ar_{a_{1}}[lld]\\ n-1 &&\vdots\\&&\mathcal A_n\ar_{a_{n}}[llu]}\end{align*}
	where the vertex of dimension $n-1$ is the middle vertex $(2,1)$.  Moreover, for $\uj\in I_l$, the representation $\tilde P_3^{\uj}$ is obtained when erasing the subquivers $\mathcal A_{j_1},\ldots,\mathcal A_{j_l}$ and decreasing the dimension of $(2,1)$ by one.  The Auslander-Reiten translate $\tau\tilde P_{3}^{(j_1,\ldots,j_l)}$ is given by
	\begin{align*}\xymatrix@R10pt@C20pt{&&(2,a_{j_1}^{-1})\ar_{a_{j_1}}[lld]\\(1,1) &&\vdots\\&&(2,a_{j_l}^{-1})\ar_{a_{j_l}}[llu]}\end{align*}
In particular, the image of the unique homomorphism $\tilde P_{2,j_i}=a^{-1}_{j_i}.\tilde P_2\to\tau\tilde P_{3}^{(j_1,\ldots,j_l)}$ has image $(2,a_{j_i}^{-1})\xrightarrow{a_{j_i}}(1,1)$ for $i=1,\ldots,l$.

The representation $\tilde P_4$ is defined by
\[\xymatrix@R40pt@C10pt{&&&&&&n-1\ar^{a_1}[llllld]\ar^{a_2}[ld]\ar^{a_n}[rrrrd]&&&&&\\&2n-3&&&&2n-3&&\hdots&&&2n-3\\
\mathcal A_2\ar^{a_2}[ru]&\hdots&\mathcal A_n\ar^{a_n}[lu]&\mathcal A_1\ar^{a_1}[rru]&\widehat{\mathcal A_2}&\mathcal A_3\ar[u]^{a_3}&\hdots&\mathcal A_n\ar^{a_n}[llu]	&\hdots&\mathcal A_2\ar^{a_2}[ru]&\hdots&\mathcal A_{n-1}\ar^{a_{n-1}}[lu]}\]
where the middle vertex is $(2,1)$. Moreover, all dimensions on the subquivers $\mathcal A_i$ are one. The arrows connecting a quiver $\mathcal A_i$ to a sink of the remaining quiver start at the unique source of $\mathcal A_i$. Now $\tilde P_{3,l}$ can be found as the representation corresponding to the subquiver
\[\xymatrix@R40pt@C10pt{&&&&&&1\ar^{a_1}[llllld]\ar^{a_{l-1}}[ld]\ar^{a_l}[d]\ar^{a_{l+1}}[rd]\ar^{a_n}[rrrrd]&&&&&\\&1&&\hdots&&1&n-1&1&\hdots&&&1\\
&&&\mathcal A_1\ar^{a_1}[rrru]&\hdots&\mathcal A_{l-1}\ar_{a_{l-1}}[ru]&\widehat{\mathcal A_l}&\mathcal A_{l+1}\ar_{a_{l+1}}[lu]&\hdots&\mathcal A_n\ar_{a_n}[lllu]	&&&&}\]
where the middle vertex is $(1,a_l)$. Thus the representation $\tilde P_4^{(1,\ldots,l)}$ is defined by

\[\xymatrix@R45pt@C10pt{&&&&&&n-1-l\ar_{a_1}[llllld]\ar^{a_{l}}[llld]\ar^{a_{l+1}}[lld]\ar^{a_n}[rrrrd]&&&&&\\&n-1-l&\hdots&n-1-l&2n-3-l&&\hdots&&\hdots&&2n-3-l\\
&\mathcal A_1\ar^{a_1}[rrru]&\hdots&\mathcal A_l\ar[ru]^{a_l}&\widehat{A}_{l+1}&\mathcal A_{l+2}\ar^{a_{l+2}}[lu]	&\hdots&\mathcal A_n\ar^{a_n}[lllu]&&\mathcal A_2\ar^{a_2}[ru]&\hdots&\mathcal A_{n-1}\ar^{a_{n-1}}[lu]}\]
where the upper vertex is again $(2,1)$. Now it is straightforward to see that $\tau \tilde P_4^{(1,\ldots,l)}=\tilde P_2^{(1,\ldots,l)}$, where $\tau$ is given by reflecting at all the sinks first and at all sources afterwards. Actually, $\tilde P_2^{(1,\ldots,l)}$  is supported at the source lying in the upper row and the $n-l$ sinks connected to it by the arrows $a_{l+1},\ldots,a_n$.

@@

 We need the following lemma analyzing the possible subrepresentations of truncated preprojective representations.
\begin{lemma}\label{le:subrep}
  Let $\uj\in I_l$. All non-trivial proper subrepresentations $U$ of $\tilde P_m^{\uj}$ are preprojective.

\end{lemma}
\begin{proof}
Without loss of generality, we choose $\{j_1,\ldots,j_l\}=\{1,\ldots,l\}$ and denote $\tilde P_m^{(l)}:=\tilde P_m^{(1,\ldots,l)}$ where $\tilde P_m^{(0)}=\tilde P_m$.

We proceed by induction. Clearly $\tilde P_m$ has only preprojective subrepresentations. We can assume without loss of generality that the subrepresentation $U$ is indecomposable. Assume that $U\subsetneq P_m^{(l)}$ is not preprojective. Then the embedding would not factor through $\tilde P_m^{(l-1)}$ by induction hypothesis.  Thus we get a commutative diagram

\[\xymatrix{0\ar[r] &\tilde P_{m-1,l}\ar[r] &  \tilde P_{m}^{(l-1)}\ar[r] & \tilde P_{m}^{(l)}\ar[r] & 0 \\
  0\ar[r]&\tilde P_{m-1,l} \ar[r]\ar@{=}[u] & U'\ar[u]\ar[r]& U\ar[r]\ar[u]& 0}\]
where the vertical maps are injective, the sequence on the bottom does not split and the representation $U'$ is preprojective by induction hypothesis. Then we have $U\in\tilde P_{m-1,l}^\perp$
because $$\Hom(\tilde P_{m-1,l},U)=\Hom(\tilde P_{m-1,l},\tilde P_{m}^{(l)})=0.$$ Moreover, $\Ext(\tilde P_{m-1,l},U)=0$ follows because the representation $\tilde P_{m-1,l}$ is preprojective and $U$ is not. We also have $\Hom(U,\tilde P_{m-1,l})=0$ for the same reason.

As the sequence does not split, this shows that $U'$ is an indecomposable preprojective subrepresentation of $\tilde P_{m}^{(l-1)}$ where the indecomposability follows from \cite[Lemma 3.12]{wei2}. Since the only exceptional representations of $K(n)$ are preprojective, we have $\Sc{\udim U}{\udim U}\leq 0$. Thus, using  $\Sc{\udim U}{\udim \tilde P_{m-1,l})}< 0$, we obtain
\[\Sc{\udim U'}{\udim U'}=\Sc{\udim U}{\udim U}+\Sc{\udim \tilde P_{m-1,l} }{\udim \tilde P_{m-1,l} }+\Sc{\udim U}{\tilde P_{m-1,l}}\leq 1+\Sc{\udim U}{\tilde P_{m-1,l}}\leq 0.\]
But this contradicts the induction hypothesis because preprojective representations do not have self-extensions.
